---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/estherc/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/estherc/ussie/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/estherc/ussie/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/estherc/ussie/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of ussie is to build a demo package for the "Building Tidy Tools" workshop at rstudio::conf(2022L). It allows you to work with European football league data supplied by the engsoccerdata package (Curley 2016).

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("estherc/ussie")
```

## Example

This is a basic example which shows you how to standardize the league tables from different countries in the engsoccerdata package:

```{r example}
library(ussie)
## Create a standardized tibble with the league stat data from the Spain
spain <- uss_make_matches(engsoccerdata::spain, "Spain")
```
