---
title: "ussie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ussie}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ussie)
library(dplyr)
```

ussie helps standardize European football data tables retrieved from the engsoccer package for each country.

```{r spain matches}

spain <- uss_make_matches(engsoccerdata::spain, "Spain")
glimpse(spain)
```

## Get data from a specific country

`uss_get_matches()` can retrieve data for a specific country (among those available) within the engsoccer dataset

```{r uss_get_matches}

spain_matches <- uss_get_matches("spain") |> glimpse()

```

We can add filtering conditions as well:

```{r uss_get_matches_filter}

spain_1987_matches <- uss_get_matches("spain", season == 1987, 
                                      home == "Real Madrid" | visitor == "Real Madrid") |>
    uss_make_teams_matches()
```

We can also accumulate seasons:
```{r cumulative seasons}

spain_1987_matches |>
  uss_make_seasons_cumulative() |>
  dplyr::arrange(team, date)

```

## Plot results over seasons

Of the countries included in `uss_countries()`, only `"england"` has data for more than one `tier`, where we can see the effects of relegation and promotion. 
You can use `uss_plot_seasons_tiers()` to look at performance over seasons, using data returned from `uss_make_seasons_final()`:

```{r leeds_norwich}
leeds_norwich <- 
  uss_get_matches("england") |>
  uss_make_teams_matches() |>
  filter(team %in% c("Leeds United", "Norwich City")) |>
  uss_make_seasons_final() |>
  arrange(team, season)
leeds_norwich
```

The default is to show the `wins` on the y-axis:

```{r plot_wins}
uss_plot_seasons_tiers(leeds_norwich)
```

You can provide an argument, `aes_y`, where you can supply an expression just as you would for ggplot2:

```{r plot_wins_losses}
uss_plot_seasons_tiers(leeds_norwich, aes_y = wins - losses)
```
